Fermi and eROSITA bubbles

### 2021-10-21 paper.tex
update

\section{Methodology}
\subsection{Assumptions and Numerical Techniques}
\begin{enumerate}
  \item \textsc{gamer-sr}
    \begin{enumerate}
      \item GPU acceleration.
      \item Using a new algorithm dedicated to the conversion between primitive and conserved variable,\
            significantly reducing numerical error caused by the non-relativistic cold disk.
    \end{enumerate}
  \item Cosmic-ray
    \begin{enumerate}
      \item We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
            as a function of $\mathbf{r}$ and $t$.
      \item We did not model the CR energy spectrum.
      \item We neglected the cooling and heating processes of CRs, such as energy losses due to synchrotron\
            and inverse Compton emission, and reacceleration in shocks.
      \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
      \item We have assumed $\mathbf{B}$ is zero within the simulation box as the field inside\
            the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
            little effect on the overall dynamics.\
            It might somewhat affect the instabilities near the bubble's surface, but that's a secondary effect.
      \item Since $\mathbf{B}$ is zero, we can also ignore the effect of cosmic-ray diffusion.
    \end{enumerate}
\end{enumerate}
We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using \
the special hydrodynamics GPU code \textsc{gamer-sr} \citep{tseng2021}.

\textsc{gamer-sr} solves mass and energy-momentum conservation laws of a special relativistic ideal fluid\
with CR

@@

\begin{subequations}
  \label{conservative-form}
  \begin{align}
   &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=0,\label{M evolution}\\
   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
   &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}} \partial_{j} U^{j},\label{D evolution}
  \end{align}
\end{subequations}
where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density,\
the momentum densities, and the reduced energy density, respectively.\
The reduced energy density is defined by subtracting the rest mass energy density of gas\
from the total energy density of gas.\
$\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas.\
$p_{\text{gas}}$ is the gas pressure.\
$p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density measured in the local rest frame.\
$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.

@@

\begin{enumerate}
\item Gravity
  \begin{enumerate}
    \item
    \item
  \end{enumerate}

@@

>>>>

\section{Methodology}
\subsection{Assumptions and Numerical Techniques}
\begin{enumerate}
  \item \textsc{gamer-sr}
    \begin{enumerate}
      \item GPU acceleration.
      \item Using a new algorithm dedicated to the conversion between primitive and conserved variable,\
            significantly reducing numerical error caused by the non-relativistic cold disk.
    \end{enumerate}
  \item Cosmic-ray
    \begin{enumerate}
      \item We treat CRs as a second fluid and solve directly for the evolution of CR pressure $p_{\text{cr}}$\
            as a function of $\mathbf{r}$ and $t$.
      \item We did not model the CR energy spectrum.
      \item We neglected the cooling and heating processes of CRs, such as energy losses due to synchrotron\
            and inverse Compton emission, and reacceleration in shocks.
      \item We have assumed cosmic-ray is passive. (i.e. $p_{\text{cr}}\ll p_{\text{gas}}$)
      \item We have assumed $\mathbf{B}$ is zero within the simulation box as the field inside\
            the bubbles should be weak due to adiabatic expansion, and thus the magnetic fields has\
            little effect on the overall dynamics.\
            It might somewhat affect the instabilities near the bubble's surface, but that's a secondary effect.
      \item Since $\mathbf{B}$ is zero, we can also ignore the effect of cosmic-ray diffusion.
    \end{enumerate}
  \item Gravity
    \begin{enumerate}
      \item Since , we have assumed the 
    \end{enumerate}
\end{enumerate}
We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using \
the special hydrodynamics GPU code \textsc{gamer-sr} \citep{tseng2021}.

\textsc{gamer-sr} solves mass and energy-momentum conservation laws of a special relativistic ideal fluid\
with CR.

@@

\begin{subequations}
  \label{conservative-form}
  \begin{align}
   &\partial_{t} D+\partial_{j} \left(DU^{j}/\gamma\right)=0,\label{D evolution}\\
   &\partial_{t} M^{i}+\partial_{j} \left(M^{i}U^{j}/\gamma+p_{\text{gas}}\delta^{ij}\right)=\
   -\rho\partial_{i}\Phi,\label{M evolution}\\
   &\partial_{t} \tilde{E}+\partial_j \left[\left(\tilde{E}+p_{\text{gas}}\right)U^{j}/\gamma\right]=0, \label{E evoltion}\\
   &\partial_{t} \left(\gamma e_{\text{cr}}\right) + \partial_{j} \left(e_{\text{cr}}U^{j}\right)=-p_{\text{cr}} \partial_{j} U^{j},\label{D evolution}
  \end{align}
\end{subequations}
where the five conserved quantities of gas $D$, $M^{i}$, and $\tilde{E}$ are the mass density,\
the momentum densities, and the reduced energy density, respectively.\
The reduced energy density is defined by subtracting the rest mass energy density of gas\
from the total energy density of gas.\
$\gamma$ and $U^{j}$ are the temporal and spatial component of four-velocity of gas.\
$\rho$ is the gas density in the local rest frame defined by $D/\gamma$.\
$p_{\text{gas}}$ is the gas pressure.\
$p_{\text{cr}}$ and $e_{\text{cr}}$ are the CR pressure and CR energy density measured in the local rest frame.\
$\Phi$ is the gravitation potential.\
$c$ is the speed of light, and $\delta^{ij}$ is the Kronecker delta notation.\
Throughout this paper, Latin indices run from 1 to 3, except when stated otherwise.

@@

\begin{enumerate}
\item Gravitational potential
  \begin{enumerate}
    \item Isothermal slab
    \item NFW potential
  \end{enumerate}

@@

\subsection{X-ray and Gamma-ray emission}
  \begin{enumerate}
    \item X-ray
       \begin{enumerate}
         \item
       \end{enumerate}
    \item Gamma-ray
       \begin{enumerate}
         \item
       \end{enumerate}
  \end{enumerate}
